hbm_paper_results

### 2024-04-19 paper_lbcc_results.Rmd
removing w/in feature assessments, cleaning up

*options: rerun from the beginning w/o UKB? Or just control for N when looking at deltas b/c UKB will always have low deltas since it's having an outsized effect on setting the distribution that both ComBatGAM and ComBatLS are targeting?

###Global Features
Look at global features

```{r}
glob_cent_deltas_df <- cent_deltas_df %>%
  dplyr::select(study, age_years, sex, participant, fs_version, paste0("delta.", vol_list_global)) %>%
  mutate(across(paste0("delta.", vol_list_global), abs, .names = "abs_{.col}"))

glob_cent_deltas_df_long <- glob_cent_deltas_df %>%
  pivot_longer(cols=starts_with("abs"), names_to="pheno", values_to = "abs_delta") %>%
  mutate(pheno=gsub("abs_delta.", "", pheno))

glob_cent_deltas_df_long %>%
  ggplot() +
  geom_boxplot(aes(y=abs_delta, color=pheno), outlier.shape = NA) + 
scale_y_continuous(limits = quantile(glob_cent_deltas_df_long$abs_delta, c(0.1, 0.9)))
```
```{r}
glob_cent_deltas_df_study <- full_join(glob_cent_deltas_df, study_info)

abs_gmv_lm <- lm(abs_delta.GMV ~ study_mean_age + study_n, data=glob_cent_deltas_df_study)
summary(abs_gmv_lm)

glob_cent_deltas_df_study %>%
  ggplot(aes(x=study_mean_age, y=abs_delta.GMV)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_abline(slope = coef(abs_gmv_lm)[["study_mean_age"]], 
              intercept = coef(abs_gmv_lm)[["(Intercept)"]])+
  theme(legend.position="none") +
  scale_y_continuous(limits = c(0, 0.1))

abs_sgmv_lm <- lm(abs_delta.sGMV ~ study_mean_age + study_n, data=glob_cent_deltas_df_study)
summary(abs_sgmv_lm)
glob_cent_deltas_df_study %>%
  ggplot(aes(x=study_mean_age, y=abs_delta.sGMV)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_abline(slope = coef(abs_sgmv_lm)[["study_mean_age"]], 
              intercept = coef(abs_sgmv_lm)[["(Intercept)"]])+
  theme(legend.position="none")+
  scale_y_continuous(limits = c(0, 0.1))

abs_wmv_lm <- lm(abs_delta.WMV ~ study_mean_age + study_n, data=glob_cent_deltas_df_study)

summary(gam(abs_delta.WMV ~ pb(study_mean_age) + study_n, data=glob_cent_deltas_df_study))

summary(abs_wmv_lm)
glob_cent_deltas_df_study %>%
  ggplot(aes(x=study_mean_age, y=abs_delta.WMV)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_abline(slope = coef(abs_wmv_lm)[["study_mean_age"]], 
              intercept = coef(abs_wmv_lm)[["(Intercept)"]])+
  theme(legend.position="none")+
  scale_y_continuous(limits = c(0, 0.1))

abs_ven_lm <- lm(abs_delta.Ventricles ~ study_mean_age + study_n, data=glob_cent_deltas_df_study)
summary(abs_ven_lm)
glob_cent_deltas_df_study %>%
  ggplot(aes(x=study_mean_age, y=abs_delta.Ventricles)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_abline(slope = coef(abs_ven_lm)[["study_mean_age"]], 
              intercept = coef(abs_ven_lm)[["(Intercept)"]])+
  theme(legend.position="none")+
  scale_y_continuous(limits = c(0, 0.1))

glob_cent_deltas_df_long <- full_join(glob_cent_deltas_df_long, study_info)

glob_cent_deltas_df_long <- glob_cent_deltas_df_long %>%
  mutate(age_diff=age_years-study_mean_age)

glob_cent_deltas_df_long %>%
  ggplot(aes(x=study_mean_age, y=abs_delta, color=pheno)) +
  geom_point(alpha=0.4) +
  geom_smooth(method="lm") +
  facet_wrap(~pheno, scales="free_y")
```

####Compare w/ Nature Paper
Compare to Nature paper age effects in sigma

```{r}
#gmv
paper_fit_gmv$param$sigma$fixef
gmv_b1 <- unname(paper_fit_gmv$param$sigma$fixef["bfpNA(AgeTransformed, powers = c(-2, 3))1"])
gmv_b2 <- unname(paper_fit_gmv$param$sigma$fixef["bfpNA(AgeTransformed, powers = c(-2, 3))2"])

#formula
gmv_age_sig <- parse(text = paste0(gmv_b1, "*x^(-2) + ", gmv_b2,"*x^(3)"))
gmv_age_sig_der <- D(gmv_age_sig,"x")

#sgmv
paper_fit_sgmv$param$sigma$fixef
sgmv_b1 <- unname(paper_fit_sgmv$param$sigma$fixef["bfpNA(AgeTransformed, powers = c(-2, -2))1"])
sgmv_b2 <- unname(paper_fit_sgmv$param$sigma$fixef["bfpNA(AgeTransformed, powers = c(-2, -2))2"])

sgmv_age_sig <- parse(text = paste0(sgmv_b1, "*x^(-2) + ", sgmv_b2,"*x^(-2)*log(x)"))
sgmv_age_sig_der <- D(sgmv_age_sig,"x")

#wmv
paper_fit_wmv$param$sigma$fixef
wmv_b1 <- unname(paper_fit_wmv$param$sigma$fixef["bfpNA(AgeTransformed, powers = c(-2, 2))1"])
wmv_b2 <- unname(paper_fit_wmv$param$sigma$fixef["bfpNA(AgeTransformed, powers = c(-2, 2))2"])

wmv_age_sig <- parse(text = paste0(wmv_b1, "*x^(-2) + ", wmv_b2,"*x^(s)"))
wmv_age_sig_der <- D(wmv_age_sig,"x")

#ven
paper_fit_ven$param$sigma$fixef
ven_b1 <- unname(paper_fit_ven$param$sigma$fixef["bfpNA(AgeTransformed, powers = c(-2, -2, -2))1"])
ven_b2 <- unname(paper_fit_ven$param$sigma$fixef["bfpNA(AgeTransformed, powers = c(-2, -2, -2))2"])
ven_b3 <- unname(paper_fit_ven$param$sigma$fixef["bfpNA(AgeTransformed, powers = c(-2, -2, -2))3"])

ven_age_sig <- parse(text = paste0(ven_b1, "*x^(-2) + ", ven_b2,"*x^(-2)*log(x) + ", ven_b3, "*x^(-2)*log(x)^(2)"))
ven_age_sig_der <- D(ven_age_sig,"x")
```
try summing abs(betas) within each pheno to get overall magnitude of age effects

```{r}
paper_sigma_age <- data.frame("pheno" = c("GMV", "sGMV", "WMV", "Ventricles"),
                              "paper_abs_betas_sum" = c(sum(abs(gmv_b1), abs(gmv_b2)), 
                                                  sum(abs(sgmv_b1), abs(sgmv_b2)),
                                                  sum(abs(wmv_b1), abs(wmv_b2)),
                                                  sum(abs(ven_b1), abs(ven_b2), abs(ven_b3))),
                              "paper_betas_sum" = c(sum(gmv_b1, gmv_b2), 
                                                  sum(sgmv_b1, sgmv_b2),
                                                  sum(wmv_b1, wmv_b2),
                                                  sum(ven_b1, ven_b2, ven_b3)),
                              "lm_beta" = c(coef(abs_gmv_lm)[["study_mean_age"]],
                                            coef(abs_sgmv_lm)[["study_mean_age"]],
                                            coef(abs_wmv_lm)[["study_mean_age"]],
                                            coef(abs_ven_lm)[["study_mean_age"]]),
                              "quick_var_range" = c((38.85552-16.93754), (0.2380905-0.1447285), (29.34474-13.4674), (17.63019-0.3520969))
                              )
paper_sigma_age %>%
  ggplot() +
  geom_col(aes(x=pheno, y=paper_abs_betas_sum, fill=pheno))

paper_sigma_age %>%
  ggplot() +
  geom_col(aes(x=pheno, y=paper_betas_sum, fill=pheno))

paper_sigma_age %>%
  ggplot() +
  geom_point(aes(x=abs(lm_beta), y=paper_betas_sum, color=pheno))

paper_sigma_age %>%
  ggplot() +
  geom_point(aes(x=abs(lm_beta), y=quick_var_range, color=pheno))
```

###W/In Cortical Features

Looking at averages w/in each cortical feature since they have different trajectories of variance across the lifespan (see Nature paper)

####Regional Volumes

```{r}
#get subject-level means
mean_vol_cent_deltas_df <- cent_deltas_df %>%
  pivot_longer(cols=any_of(paste0("delta.", vol_list_regions)), names_to="pheno", values_to = "centile") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_delta_vol_cent=(mean(centile))*100, #convert units to centiles space
            abs_mean_delta_vol_cent=(mean(abs(centile)))*100) %>%
  dplyr::select(!(starts_with("delta")))

mean_vol_cent_deltas_df_study <- full_join(mean_vol_cent_deltas_df, study_info)

abs_vol_lm <- lm(abs_mean_delta_vol_cent ~ study_mean_age + study_n, data=mean_vol_cent_deltas_df_study)
summary(abs_vol_lm)

mean_vol_cent_deltas_df_study %>%
  ggplot(aes(x=study_mean_age, y=abs_mean_delta_vol_cent)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_abline(slope = coef(abs_vol_lm)[["study_mean_age"]], 
              intercept = coef(abs_vol_lm)[["(Intercept)"]])+
  theme(legend.position="none")
```

####Regional Thickness

```{r}
#get subject-level means
mean_ct_cent_deltas_df <- cent_deltas_df %>%
  pivot_longer(cols=any_of(paste0("delta.", ct_list)), names_to="pheno", values_to = "centile") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_delta_ct_cent=(mean(centile))*100, #convert units to centiles space
            abs_mean_delta_ct_cent=(mean(abs(centile)))*100) %>%
  dplyr::select(!(starts_with("delta")))

mean_ct_cent_deltas_df_study <- full_join(mean_ct_cent_deltas_df, study_info)

abs_ct_lm <- lm(abs_mean_delta_ct_cent ~ study_mean_age + study_n, data=mean_ct_cent_deltas_df_study)
summary(abs_ct_lm)

mean_ct_cent_deltas_df_study %>%
  ggplot(aes(x=study_mean_age, y=abs_mean_delta_ct_cent)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_abline(slope = coef(abs_ct_lm)[["study_mean_age"]], 
              intercept = coef(abs_ct_lm)[["(Intercept)"]])+
  theme(legend.position="none")
```

much bigger than anticipated based on Nature paper!!? is combatLS overfitting?

```{r}
#get subject-level means
mean_ct_cent_gamlss_df <- gamlss_centile_df.clean %>%
  pivot_longer(cols=any_of(ct_list), names_to="pheno", values_to = "centile") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_ct_cent=(mean(centile))*100)
```

```{r}
mean_ct_cent_gamlss_df <- full_join(mean_ct_cent_gamlss_df, study_info)
summary(lm(mean_ct_cent ~ study_mean_age, data=mean_ct_cent_gamlss_df))
summary(lm(mean_ct_cent ~ study_mean_age + study_n, data=mean_ct_cent_gamlss_df))

# mean_ct_cent_gamlss_df %>%
#   ggplot(aes(x=study_mean_age, y=mean_ct_cent)) +
#   geom_point(aes(color=study), alpha=0.2) +
#   geom_smooth(method = "lm") +
#   theme(legend.position="none")

#get subject-level means
mean_ct_cent_gam_df <- gam_centile_df.clean %>%
  pivot_longer(cols=any_of(ct_list), names_to="pheno", values_to = "centile") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_ct_cent=(mean(centile))*100)

mean_ct_cent_gam_df <- full_join(mean_ct_cent_gam_df, study_info)
summary(lm(mean_ct_cent ~ study_mean_age, data=mean_ct_cent_gam_df))
summary(lm(mean_ct_cent ~ study_mean_age + study_n, data=mean_ct_cent_gam_df))

# mean_ct_cent_gam_df %>%
#   ggplot(aes(x=study_mean_age, y=mean_ct_cent)) +
#   geom_point(aes(color=study), alpha=0.2) +
#   geom_smooth(method = "lm") +
#   theme(legend.position="none")
```

####Regional SA

```{r}
#get subject-level means
mean_sa_cent_deltas_df <- cent_deltas_df %>%
  pivot_longer(cols=any_of(paste0("delta.", sa_list)), names_to="pheno", values_to = "centile") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_delta_sa_cent=(mean(centile))*100, #convert units to centiles space
            abs_mean_delta_sa_cent=(mean(abs(centile)))*100) %>%
  dplyr::select(!(starts_with("delta")))

mean_sa_cent_deltas_df_study <- full_join(mean_sa_cent_deltas_df, study_info)

abs_sa_lm <- lm(abs_mean_delta_sa_cent ~ study_mean_age + study_n, data=mean_sa_cent_deltas_df_study)
summary(abs_sa_lm)

mean_sa_cent_deltas_df_study %>%
  ggplot(aes(x=study_mean_age, y=abs_mean_delta_sa_cent)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_abline(slope = coef(abs_sa_lm)[["study_mean_age"]], 
              intercept = coef(abs_sa_lm)[["(Intercept)"]])+
  theme(legend.position="none")
```

####Compare

```{r}
df_list.tmp <- list(mean_sa_cent_deltas_df_study, mean_ct_cent_deltas_df_study, mean_vol_cent_deltas_df_study)
all_reg_deltas <- df_list.tmp %>% reduce(full_join)
```

```{r}
all_reg_deltas_long <- all_reg_deltas %>%
  pivot_longer(cols=starts_with("abs_mean_delta"), names_to="pheno_type", values_to = "abs_cent_delta") %>%
  mutate(pheno_type=gsub("abs_mean_delta_|_cent", "", pheno_type))

all_reg_deltas_long %>%
  ggplot() +
  geom_boxplot(aes(y=abs_cent_delta, fill=pheno_type))
```

```{r}
delta_sum.df_merged %>%
  ggplot(aes(x=study_mean_age_yrs, y=study_mean_delta)) +
  geom_count(aes(size=study_n)) +
  geom_smooth(method="lm")
delta_sum.df_merged %>%
  ggplot(aes(x=study_mean_age_yrs, y=study_mean_abs.delta)) +
  geom_count(aes(size=study_n)) +
  geom_smooth(method="lm")

age_effects.plt.p <- summary(lm((site_mean_abs.delta*100) ~ sex_prop_Female + site_n + site_mean_age_yrs, data=delta_sum.df_merged))$coef["site_mean_age_yrs", "Pr(>|t|)"]
age_effects.plt.slope <- summary(lm((site_mean_abs.delta*100) ~ sex_prop_Female + site_n + site_mean_age_yrs, data=delta_sum.df_merged))$coef["site_mean_age_yrs", "Estimate"]

age_effects.plt <- delta_sum.df_merged %>%
  ggplot(aes(x=site_mean_age_yrs, y=(site_mean_abs.delta*100))) +
  geom_count(aes(size=site_n, color=sex_prop_Female)) +
  paletteer::scale_color_paletteer_c("ggthemes::Blue", name = "Proportion \nFemale") +
  geom_smooth(method="lm", color="#2A5783FF") +
  theme_linedraw(base_size = 11) +
  annotate("text", x=60, y=4, label=paste("Mean Age \nEstimate =", round(age_effects.plt.slope, 4), "\np =", round(age_effects.plt.p, 4)), size=3) +
  labs(size="site N", x = "Mean Age (Years)", y = "Mean Absolute Difference in Centile Scores") +
  theme(axis.title.x=element_blank())

age_effects.plt.p <- summary(lm((site_mean_delta*100) ~ sex_prop_Female + site_n + site_mean_age_yrs, data=delta_sum.df_merged))$coef["site_mean_age_yrs", "Pr(>|t|)"]
age_effects.plt.slope <- summary(lm((site_mean_delta*100) ~ sex_prop_Female + site_n + site_mean_age_yrs, data=delta_sum.df_merged))$coef["site_mean_age_yrs", "Estimate"]

age_effects.plt.null <- delta_sum.df_merged %>%
  ggplot(aes(x=site_mean_age_yrs, y=(site_mean_delta*100))) +
  geom_count(aes(size=site_n, color=sex_prop_Female)) +
  paletteer::scale_color_paletteer_c("ggthemes::Blue", name = "Proportion \nFemale") +
  geom_smooth(method="lm", color="#2A5783FF") +
  theme_linedraw(base_size = 11) +
  annotate("text", x=60, y=-0.3, label=paste("Mean Age \nEstimate =", round(age_effects.plt.slope, 4), "\np =", round(age_effects.plt.p, 4)), size=3) +
  labs(size="site N", x = "Mean Age (Years)", y = "Mean Difference in Centile Scores")

#add prediction to df
delta_sum.df_merged$abs.delta_pred <- predict(full.delta.age.fit)

full.delta.age.fit.df <- data.frame(x=ggeffects::ggemmeans(full.delta.age.fit, terms="site_mean_age_yrs")$x,
                                    predicted=ggeffects::ggemmeans(full.delta.age.fit, terms="site_mean_age_yrs")$predicted,
                                    conf.low=ggeffects::ggemmeans(full.delta.age.fit, terms="site_mean_age_yrs")$conf.low,
                                    conf.high=ggeffects::ggemmeans(full.delta.age.fit, terms="site_mean_age_yrs")$conf.high)
full.delta.age.fit.df <- full.delta.age.fit.df %>%
  mutate(predicted = predicted*100,
         conf.low=conf.low*100,
         conf.high=conf.high*100)

marg.age_effects.plt <- ggplot() +
  geom_count(data=delta_sum.df_merged, aes(x=site_mean_age_yrs, y=(abs.delta_pred*100), size=site_n, color=sex_prop_Female)) +
  paletteer::scale_color_paletteer_c("ggthemes::Blue", name = "Proportion \nFemale") +
  geom_line(aes(x=full.delta.age.fit.df$x, y = full.delta.age.fit.df$predicted), size = 0.7, color="#2A5783FF") +
  geom_ribbon(aes(x=full.delta.age.fit.df$x,y= NULL, ymin= full.delta.age.fit.df$conf.low, ymax= full.delta.age.fit.df$conf.high), alpha=0.1, fill="#2A5783FF") +
  theme_linedraw(base_size = 11) +
  labs(size="site N", x = "Mean Age (Years)", y = "Predicted Mean Absolute Difference in Centile Scores")
```

are studies w older subjects changing more because there are fewer of them?
check for association between study size and age
```{r}
summary(lm(study_mean_age_yrs ~ study_n, data=delta_sum.df_merged)) #study size is associated with age, but assoc. remains when controlling for size
```

```{r}
cent_deltas_df %>%
  ggplot() +
  geom_histogram(aes(x=age_days)) +
  labs(title="subject distribution across age")

delta_sum.df_merged %>%
  ggplot() +
  geom_histogram(aes(x=study_mean_age_yrs)) +
  labs(title="study distribution across age")
```

##Prop Female

```{r}
ggplot(delta_sum.df_merged) +
  geom_histogram(aes(x=sex_prop_Female))
```

ComBatGAM mean centile ~ % female

```{r}
gam_centile_study.mean.df <- gam_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile") %>%
  group_by(study) %>%
  summarize(mean_gam_cent=mean(centile),
            mean_gam_abs_cent=mean(abs(centile)))

gam_centile_study.mean.df2 <- left_join(gam_centile_study.mean.df, delta_sum.df_merged)

gam.prop.f.test <- lm(mean_gam_cent ~ sex_prop_Female + study_n + study_mean_age, data=gam_centile_study.mean.df2)
summary(gam.prop.f.test)
gam.prop.f.test2 <- lm(mean_gam_abs_cent ~ sex_prop_Female + study_n + study_mean_age, data=gam_centile_study.mean.df2)
summary(gam.prop.f.test2)

ggplot(gam_centile_study.mean.df2, aes(x=sex_prop_Female, y=mean_gam_cent)) +
  geom_point() +
  geom_smooth(method="lm")
```

ComBatLS mean centile ~ % female

```{r}
gamlss_centile_study.mean.df <- gamlss_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile") %>%
  group_by(study) %>%
  summarize(mean_gamlss_cent=mean(centile),
            mean_gamlss_abs_cent=mean(abs(centile)))

gamlss_centile_study.mean.df2 <- left_join(gamlss_centile_study.mean.df, delta_sum.df_merged)

gamlss.prop.f.test <- lm(mean_gamlss_cent ~ sex_prop_Female + study_n + study_mean_age, data=gamlss_centile_study.mean.df2)
summary(gamlss.prop.f.test)
gamlss.prop.f.test2 <- lm(mean_gamlss_abs_cent ~ sex_prop_Female + study_n + study_mean_age, data=gamlss_centile_study.mean.df2)
summary(gamlss.prop.f.test2)

ggplot(gamlss_centile_study.mean.df2, aes(x=sex_prop_Female, y=mean_gamlss_cent)) +
  geom_point() +
  geom_smooth(method="lm")
```

```{r}
gamlss_centile_site.mean.df3 <- gamlss_centile_site.mean.df2 %>%
  mutate(combat = "gamlss") %>%
  rename(mean_cent = mean_gamlss_cent)
gam_centile_site.mean.df3 <- gam_centile_site.mean.df2 %>%
  mutate(combat = "gam") %>%
  rename(mean_cent = mean_gam_cent)

site_lvl_mean_cents <- full_join(gamlss_centile_site.mean.df3, gam_centile_site.mean.df3)

site_lvl_mean_cents %>%
  ggplot(aes(x=sex_prop_Female, y=mean_cent, color=combat, fill=combat)) +
  geom_point(alpha=0.4) +
  geom_smooth(method="lm") +
  ylab("within-site mean centile")
```

```{r}
gamlss_centile_df.mean %>%
  ggplot() + 
  geom_violin(aes(x=sex, y=mean_cent))
gamlss_centile_df.mean$combat <- "gamlss"

gam_centile_df.mean %>%
  ggplot() + 
  geom_violin(aes(x=sex, y=mean_cent))
gam_centile_df.mean$combat <- "gam"

subj.mean.cents <- full_join(gamlss_centile_df.mean, gam_centile_df.mean)

subj.mean.cents %>%
  ggplot() + 
  geom_boxplot(aes(x=sex, y=mean_cent, fill=combat))

#add sex prop
site.info <- delta_sum.df_merged %>%
  dplyr::select(site, sex_prop_Female, site_n)

subj.mean.cents2 <- left_join(subj.mean.cents, site.info)
subj.mean.cents2 %>%
  ggplot(aes(x=sex_prop_Female, y=mean_cent, color=sex)) +
  geom_point(aes(size=site_n)) +
  geom_smooth(method="lm")+
  facet_wrap(~combat)

subj.mean.cents2 %>%
  ggplot(aes(x=sex_prop_Female, y=mean_cent, color=combat, fill=combat)) +
  # geom_point(alpha=0.4) +
  geom_smooth(method="lm") +
  ylab("within-subject mean centile")
```

delta ~ % female

```{r}
# %female
summary(lm(site_mean_abs.delta ~ sex_prop_Female, data=delta_sum.df_merged))
summary(lm(site_mean_delta ~ sex_prop_Female, data=delta_sum.df_merged))
summary(lm(site_mean_delta ~ sex_prop_Female + site_n, data=delta_sum.df_merged)) #add site size covariate
summary(lm(site_mean_delta ~ sex_prop_Female + site_n + site_mean_age, data=delta_sum.df_merged)) #add site size & age covariates
full.delta.sex.fit <- lm(site_mean_delta ~ sex_prop_Female + site_n + site_mean_age, data=delta_sum.df_merged) #scaling for plot

sjPlot::plot_model(full.delta.sex.fit, type = "pred", terms = "sex_prop_Female") 
```

```{r}
delta_sum.by.sex.df %>%
  ggplot(aes(x=sex, y=(mean_delta*100), color=as.factor(majority), fill=as.factor(majority))) +
  geom_count(aes(shape=as.factor(majority), size=sex_prop), alpha=0.5) +
  geom_line(aes(group=site))
```

```{r}
delta_sum.df_merged %>%
  ggplot(aes(x=sex_prop_Female, y=site_mean_delta)) +
  geom_count(aes(size=site_n)) +
  geom_smooth(method="lm")
delta_sum.df_merged %>%
  ggplot(aes(x=sex_prop_Female, y=site_mean_abs.delta)) +
  geom_count(aes(size=site_n)) +
  geom_smooth(method="gam")

sex_effects.plt.p <- summary(lm((site_mean_delta*100) ~ sex_prop_Female + site_n + site_mean_age, data=delta_sum.df_merged))$coef["sex_prop_Female", "Pr(>|t|)"]
sex_effects.plt.slope <- summary(lm((site_mean_delta*100) ~ sex_prop_Female + site_n + site_mean_age, data=delta_sum.df_merged))$coef["sex_prop_Female", "Estimate"]

sex_effects.plt <- delta_sum.df_merged %>%
  mutate(site_mean_delta=site_mean_delta*100) %>%
  ggplot(aes(x=sex_prop_Female, y=site_mean_delta)) +
  geom_count(aes(size=site_n, color=site_mean_age_yrs)) +
  geom_smooth(method="lm",
              color="#24693DFF") +
  paletteer::scale_color_paletteer_c("ggthemes::Green", name = "Mean Age \n(Years)") +
  theme_linedraw(base_size = 11) +
  labs(size="site N", x = "Proportion Female", y = "Mean Difference in Centile Scores") +
  theme(axis.title.y=element_blank()) +
  annotate("text", x=0.25, y=-0.3, label=paste("Proportion Female \nEstimate =", round(sex_effects.plt.slope, 4), "\np =", round(sex_effects.plt.p, 4)), size=3) +
  guides(size = "none")

sex_effects.plt.p <- summary(lm((site_mean_abs.delta*100) ~ sex_prop_Female + site_n + site_mean_age, data=delta_sum.df_merged))$coef["sex_prop_Female", "Pr(>|t|)"]
sex_effects.plt.slope <- summary(lm((site_mean_abs.delta*100) ~ sex_prop_Female + site_n + site_mean_age, data=delta_sum.df_merged))$coef["sex_prop_Female", "Estimate"]

sex_effects.plt.null <- delta_sum.df_merged %>%
  ggplot(aes(x=sex_prop_Female, y=(site_mean_abs.delta*100))) +
  geom_count(aes(size=site_n, color=site_mean_age_yrs)) +
  geom_smooth(method="lm", color="#24693DFF") +
  paletteer::scale_color_paletteer_c("ggthemes::Green", name = "Mean Age \n(Years)") +
  theme_linedraw(base_size = 11) +
  labs(size="site N") +
    annotate("text", x=0.25, y=4, label=paste("Proportion Female \nEstimate =", round(sex_effects.plt.slope, 4), "\np =", round(sex_effects.plt.p, 4)), size=3) +
  theme(axis.title=element_blank()) +
  guides(size = "none")

#add prediction to df
delta_sum.df_merged$delta_pred <- predict(full.delta.sex.fit)

full.delta.sex.fit.df <- data.frame(x=ggeffects::ggemmeans(full.delta.sex.fit, terms="sex_prop_Female")$x,
                                    predicted=ggeffects::ggemmeans(full.delta.sex.fit, terms="sex_prop_Female")$predicted,
                                    conf.low=ggeffects::ggemmeans(full.delta.sex.fit, terms="sex_prop_Female")$conf.low,
                                    conf.high=ggeffects::ggemmeans(full.delta.sex.fit, terms="sex_prop_Female")$conf.high)
full.delta.sex.fit.df <- full.delta.sex.fit.df %>%
  mutate(predicted = predicted*100,
         conf.low=conf.low*100,
         conf.high=conf.high*100)

marg.sex_effects.plt <- ggplot() +
  geom_count(data=delta_sum.df_merged, aes(x=sex_prop_Female, y=(delta_pred*100), size=site_n, color=site_mean_age_yrs)) +
  geom_line(aes(x=full.delta.sex.fit.df$x, y = full.delta.sex.fit.df$predicted), size = 0.7, color="#24693DFF") +
  geom_ribbon(aes(x=full.delta.sex.fit.df$x,y= NULL, ymin= full.delta.sex.fit.df$conf.low, ymax= full.delta.sex.fit.df$conf.high), alpha=0.1, fill="#24693DFF") +
  paletteer::scale_color_paletteer_c("ggthemes::Green", name = "Mean Age \n(Years)") +
  theme_linedraw(base_size = 11) +
  labs(size="site N", x = "Proportion Female", y = "Predicted Mean Difference in Centile Scores")

delta_sum.by.sex.df %>%
  ggplot(aes(x=sex, y=(mean_delta*100))) +
  geom_boxplot()
```

```{r}
# age*%female
summary(lm(site_mean_abs.delta ~ site_mean_age_yrs*sex_prop_Female, data=delta_sum.df_merged))
summary(lm(site_mean_delta ~ site_mean_age_yrs*sex_prop_Female, data=delta_sum.df_merged))
```

```{r}
cent_deltas_df %>%
  ggplot(aes(x=age_days, y=(delta.GMV*100))) +
  geom_point(alpha=0.4) +
  geom_smooth(method="lm")

cent_deltas_df %>%
  ggplot(aes(x=delta.lh_SA_fusiform*100, color=sex, fill=sex)) +
  geom_histogram(aes(y=after_stat(c(
      count[group==1]/sum(count[group==1]),
      count[group==2]/sum(count[group==2])
    )*100)), alpha=0.4, position="identity", bins=60) +
  ylab("Percentage")

cent_deltas_df %>%
  ggplot(aes(x=age_days, y=delta.rh_Vol_supramarginal*100, color=sex, fill=sex)) +
  geom_point(alpha=0.3) +
  geom_smooth(method="lm")

cent_deltas_df %>%
  ggplot(aes(x=age_days, y=delta.rh_Vol_temporalpole*100, color=sex, fill=sex)) +
  geom_point(alpha=0.4) +
  geom_smooth(method="lm")
```

>>>>

control for N when looking at deltas b/c UKB will always have low deltas since it's having an outsized effect on setting the distribution that both ComBatGAM and ComBatLS are targeting?
